Contracts for Contracts

### 2023-06-07 paper/related_work.tex
misc

\subsubsection*{\textbf{Behavioral Contracts}}

Eiffel the ``design-by-contract'' methodology \cite{DBLP:books/ph/Meyer91, DBLP:conf/tools/Meyer98a}

@@

\subsubsection*{\textbf{Smart Contracts}}

core calculus of Solidity-like languages \cite{Sergey2021, DBLP:conf/esorics/BartolettiGM19, DBLP:conf/fc/CrafaPZ19}

>>>>

\paragraph{Behavioral Contracts and Runtime Verification}
Eiffel the ``design-by-contract'' methodology \cite{DBLP:books/ph/Meyer91, DBLP:conf/tools/Meyer98a}

@@

A closely related work to our temporal contracts and monitoring is interface automata \cite{DBLP:conf/sigsoft/AlfaroH01}.
\todo{difference}

\paragraph{Smart Contracts}
core calculus of Solidity-like languages \cite{Sergey2021, DBLP:conf/esorics/BartolettiGM19, DBLP:conf/fc/CrafaPZ19}
